%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2.5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape ROHIT KUMAR} \\ \vspace{.5 em}
    KIET Group of Institutions, Ghaziabad, 201206 \\ \vspace{.5em}
    \small \raisebox{-0.5em\height}\faPhone\ 99580229633 ~ \href{mailto:x@gmail.com}{\raisebox{-0.1em\height}\faEnvelope\  \underline{anujrohitkumar3010@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{https://www.linkedin.com/in/rohit-kumar-77559b204/}}  ~
    \href{https://leetcode.com/anujrohitkumar3010/}{https://leetcode.com/anujrohitkumar3010/}
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{ https://github.com/Rohitanuj}}
    \vspace{-2em}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KIET Group of Institutions, Ghaziabad}{Nov 2020 -- May 2024}
      {Bachelor of Technology in Computer Science}{Ghaziabad, UP}
  \resumeSubHeadingListEnd
   \resumeSubheading
      {AMRIT PUBLIC SCHOOL}{2017 -- 2019}
      {Intermediate}{Mau, UP}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{3}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Software Engineering
                \item Algorithms and Analysis
                \item Database Management System
                \item Computer Networks
                \item Operating System
            \end{itemize}
        \end{multicols}
        \vspace*{1.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cisco Virtual Internship}{May 2023 -- August 2023}
      {Intern}{Virtual}
      \resumeItemListStart
        \resumeItem{Completed Modules on Cloud Security, Introduction to CyberSecurity, Introduction to Packet Tracer, Cybersecurity essentials.Conducted Study on the imaginary Network, evaluated its vulnerability and Developed solution Network overcoming its weakness.}
        \resumeItem{As a Final deliverable for Project, Implemented a Network in Cisco Packet Tracer. Composed a PPT explaining the modules used in that network in depth.}
      \resumeItemListEnd
    \resumeSubheading
      {CPI-D Internship}{Aug 2022 -- August 2022}
      {Intern}{KIET,Ghaziabad}
      \resumeItemListStart
        \resumeItem{Learned About Java Programming and OOPS Concepts.Completed Mooc Course on Great Learning Namely OOPS By Great Learning.}
        \resumeItem{Build a GUI Based Application, Namely Temperature Converter.This was Created on Netbeans IDE 15 Harnessing Learnings of Internship.}
        \vspace{-3.0em}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{+1.em}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-0.5em}
    \resumeSubHeadingListStart
      \resumeProjectHeading{\textbf{MySQL Injection Prevention } $|$ \emph{PHP,React,Adobe,MySQL}}{Aug 2023-Ongoing}
          \resumeItemListStart
          
            \resumeItem{This is Group Project. Devloped Front End of the Project Using HTML,CSS AND JS.}
            \resumeItem{Project aim to provide effective Waste Management. Concept is Implemented Using IOT}
            \resumeItem{Aim is to track the Fill level of trash cans and use that information to automate the Process of Waste Management. }
          \resumeItemListEnd
          \vspace{-1em}
      \resumeProjectHeading
          {\textbf{Avon: MyFood App Website} $|$ \emph{HTML,CSS,JS,React,VS CODE}}{Feb 2023-Apr 2023}
          \resumeItemListStart
            \resumeItem{Devised the Front End of Food Ordering Website using HTML, CSS AND JAVASCRIPT.}
            \resumeItem{Focused on responsive Web design and Cross Devices Compatibility.}
            \resumeItem{As a front end website, it focuses on User interface and User Experience. Used Fontawesome icons to improve Look and functionality.}
          \resumeItemListEnd
          \vspace{-1.0em}
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java Basics, HTML/CSS, JavaScript, MySQL,Python ,GoLang} \\
     \textbf{Developer Tools}{: VS Code, Github , Google Cloud Platform,NetBeans IDE, Py Charm} \\
     \textbf{Miscellaneous}{:Cloud Computing Essentials, Cybersecurity Basics} \\
    }}
 \end{itemize}
 \vspace{-1em}
%-----------PROGRAMMING SKILLS-----------
\section{Achievements/Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \resumeItemListStart
            \resumeItem{●350+ problems on Leetcode/Secured 2663th Rank in Leetcode Weekly contest 342 }
            \resumeItem{●5 star in Problem solving and in JAVA on HackerRank}
            \resumeItem{●CERTIFICATION 1: Data Structures - by University of California San Diego and offered through Coursera. (06/2023).}
            \resumeItem{●CERTIFICATION 2:Algorithmic Toolbox - by University of California San Diego and offered through Coursera.(2021)}
            \resumeItem{●CERTIFICATION 3:Java Programming: Solving Problems with Software- by Duke University and offered through Coursera.(2021)}
            \resumeItem●CERTIFICATION 4: Object Oriented Programming by UC San Diego on Coursera(2022)
          \resumeItemListEnd 
    \resumeSubHeadingListEnd

\vspace{-1em}
\end{document}
